%-------------------------
% Resume in LaTeX
% Author: Priyanshu Sharma
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Choose your font here
% Example: Fira Sans
% \usepackage[sfdefault]{FiraSans}
% Example: Cormorant Garamond
% \usepackage{CormorantGaramond}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Priyanshu Sharma} \\ \vspace{1pt}
    \textit{Final Year Undergraduate Student} \\
    \href{mailto:pskara39@gmail.com}{{pskara39@gmail.com}} $|$ \href{tel:9602823283}{{9602823283}} $|$
    \href{https://www.linkedin.com/in/priyanshusharma24}{{LinkedIn}}
    $|$ \href{https://github.com/codekashyap}{GitHub} $|$
    \href{https://sites.google.com/ds.study.iitm.ac.in/priyanshu-sharma/home?authuser=0}{Website}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Institute of Technology, Nirma University}{Ahmedabad, GJ}
{Bachelor of Technology in Electrical Engineering}{Oct. 2020 - May 2024}
\resumeSubheading
{Indian Institute of Technology Madras}{Online Degree}
{Bachelor of Science in Data Science and Applications (BSc)}{Jan. 2022 - Dec. 2024}
\resumeSubheading
{Allen Career Institute}{Kota, RJ}
{JEE Coaching}{April. 2019 - March 2020}
\resumeSubheading
{Himalayan International School}{Patna, BR}
{CBSE XII}{April. 2017 - March 2019}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Ernst and Young}{June 2023 - July 2023}
{Summer Intern, Project: Digital Transformation for IOCL}{Gurugram, HR}
\resumeItemListStart
\resumeItem{Coordinated with a team to develop software for optimizing crude shipping operations, vessel scheduling, and tonnage systems, leading to potential cost savings for clients.}
\resumeItem{Gained practical experience in utilizing different optimization algorithms for vessel scheduling, leading to enhanced efficiency and accuracy in the scheduling process.}
\resumeItem{Conducted trigger testing using SQL to ensure the correctness and robustness of the underlying database logic.}
\resumeItem{Applied business and consulting skills to the project, gaining insights into the interaction between technology and real-world operations.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Wind Turbine Energy Prediction Model}}
\resumeProjectHeadingEnd
\resumeItemListStart
\resumeItem{Developed a supervised ML model based on historical SCADA data to predict wind turbine energy generation.}
\resumeItem{Built and deployed a web application on an AWS cloud server, allowing users to input relevant parameters and obtain accurate energy generation forecasts.}
\resumeItem{Technologies used: Python, NumPy, Pandas, Seaborn, SKLearn, Linear Regression, Random Forest Regressor, XG Boost, Flask, HTML, AWS.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Movies Recommendation System}}
\resumeProjectHeadingEnd
\resumeItemListStart
\resumeItem{Created a website using Streamlit, which recommends 5 similar movies to the user based on their choice.}
\resumeItem{Pre-processed the dataset by converting movie details into proper tags using techniques such as stemming and
vectorization.}
\resumeItem{Technologies used: Python and its libraries using NumPy, Pandas, SKLearn, NLP, and Streamlit.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Data Science}{: Machine Learning, Deep Learning, Data Analysis, Statistics, Web Scraping, AWS Cloud, NLP} \\
\textbf{Programming}{: Python, C++, Data Structures, Algorithms, Object-Oriented Programming, SQL, DBMS} \\
\textbf{Tools}{: VS Code, SKLearn, TensorFlow, Jupyter, NumPy, Pandas, Matplotlib, PostgreSQL, DBeaver, MS Excel, MS PowerPoint, GitHub}
}}
\end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{BCG Gamma Data Science Virtual Experience Program on Forage $|$ The Complete Data Science by Udemy $|$ SQL
(Intermediate) by HackerRank $|$ Pandas by Kaggle
}
\end{itemize}

%-----------SUMMARY-----------
\section{Summary}
\small{Seeking an entry-level position in the dynamic realm of Technology, with a focus on Data Science and Analytics. Proficient in data handling, visualization, and employing statistical techniques. Skilled in algorithmic problem-solving, poised to contribute to innovative, data-driven projects. Eager to leverage AI skills to drive profitable business transformations.}

%-------------------------------------------
\end{document}
